Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-03-16 paper/ms.tex
Fix time of circular velocity curve

We computed the circular velocity curve of our model using the \texttt{AGAMA}
package \citep{2019MNRAS.482.1525V}. We fit the baryonic component (stellar disk,
bulge, gas, and newly formed stars) with an axisymmetric cylindrical spline with
$20$ grid points in both the radial and vertical direction spanning $0.2$ to
$50\,\textrm{kpc}$ in the radial direction and from $0.02$ to $10\,\textrm{kpc}$
in the vertical direction. We fit the dark matter halo using a spherically
symmetric multipole fit with a maximum angular harmonic coefficient of $l=2$. We
plot the circular velocity curve in Fig.~\ref{fig:vcirc} compared to
observational estimates \citep{2019ApJ...871..120E}. The \SMUGGLE{} disk (which
includes additional mass in the form of gas) has a slightly higher circular
velocity than the \Nbody{} disk which, itself, is slightly higher than the
observational estimates. Overall, though, the circular velocity curves between
our model and that observed in the Milky Way are broadly consistent.

@@

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/vcirc.pdf}
    \caption{The circular velocity curve of our initial setups. This
    curve is shown for the \Nbody{} run (blue) and the \SMUGGLE{} run (orange)
    compared to observational estimates for the Milky
    Way \citep{2019ApJ...871..120E}. We see that the circular velocity curve for
    both runs is marginally larger than the Milky Way's, but still comparable. The
    \SMUGGLE{} circular velocity curve is larger than the \Nbody{} curve due to the
    additional mass in the gas phase.}
    \label{fig:vcirc}
\end{figure}

>>>>

We computed the circular velocity curve of our model using the \texttt{AGAMA}
package \citep{2019MNRAS.482.1525V}. We fit the baryonic component (stellar disk,
bulge, gas, and newly formed stars) with an axisymmetric cylindrical spline with
$20$ grid points in both the radial and vertical direction spanning $0.2$ to
$50\,\textrm{kpc}$ in the radial direction and from $0.02$ to $10\,\textrm{kpc}$
in the vertical direction. We fit the dark matter halo using a spherically
symmetric multipole fit with a maximum angular harmonic coefficient of $l=2$. We
plot the circular velocity curve {\bf at $t=1\,\textrm{Gyr}$} in Fig.~\ref{fig:vcirc} compared to
observational estimates \citep{2019ApJ...871..120E}. The \SMUGGLE{} disk (which
includes additional mass in the form of gas) has a slightly higher circular
velocity than the \Nbody{} disk which, itself, is slightly higher than the
observational estimates. Overall, though, the circular velocity curves between
our model and that observed in the Milky Way are broadly consistent.

@@

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/vcirc.pdf}
    \caption{The circular velocity curve of our setups {\bf at $t=1\,\textrm{Gyr}$}.
    This curve is shown for the \Nbody{} run (blue) and the \SMUGGLE{} run
    (orange) compared to observational estimates for the Milky Way
    \citep{2019ApJ...871..120E}. We see that the circular velocity curve for
    both runs is marginally larger than the Milky Way's, but still comparable.
    The \SMUGGLE{} circular velocity curve is larger than the \Nbody{} curve due
    to the additional mass in the gas phase.}
    \label{fig:vcirc}
\end{figure}
